### 2020-10-20 submission/manuscript.Rmd
Create Figures 2 and S2

**How do communities change when rare ASVs are removed?** Removing rare ASVs will reduce the number of observed ASVs and proportionally increase the relative abundance of the remaining ASVs. The result was expected to be a loss of information contained within each sample. To quantify the effect of removing rare ASVs on the information contained within each sample, I varied the minimum abundance threshold to simulate removing ASVs of varying rarity from each sample. The number of ASVs in each sample decreased by between `r oxford_comma(asv_s_two, 1)`% when removing those ASVs that only appeared once and by between `r oxford_comma(asv_s_eleven, 1)`% when removing those that appeared ten or fewer times from each sample (Figure X). Similarly, the Shannon diversity decreased by between `r oxford_comma(asv_h_two, 1)`% when removing ASVs that only appeared once and by between `r oxford_comma(asv_s_eleven, 1)`% when removing ASVs that appeared ten or fewer times from each sample (Figure X). Next, I assigned the ASVs to OTUs to assess the impact of removing rare ASVs on higher level taxonomic groupings that are commonly used in microbial ecology studies. Although pooling similar ASVs into OTUs reduced the impact of removing the rare ASVs relative to the ASV-based analysis, the minimum abundance threshold still decreased the number of observed OTUs and the diversity decreased relative to the original community (**Figure 1**). In contrast to the number of ASVs or OTUs and their diversity, the Kullback–Leibler divergence compares the relative abundance of each ASV or OTU between representations of the community. I calculated the Kullback–Leibler divergence from the full to pruned communities when rare ASVs were removed. As the threshold for removing ASVs increased, the amount of information lost also increased for both ASVs and OTUs (Figure X). The relative loss of information was generally lower for OTUs than than it was for ASVs. Removing rare ASVs, regardless of abundance threshold, had profound impacts on the representation of the communities.

>>>>

**How do communities change when rare ASVs are removed?** Removing rare ASVs will reduce the number of observed ASVs and proportionally increase the relative abundance of the remaining ASVs. The result was expected to be a loss of information contained within each sample. To quantify the effect of removing rare ASVs on the information contained within each sample, I varied the minimum abundance threshold to simulate removing ASVs of varying rarity from each sample. The number of ASVs in each sample decreased by between `r oxford_comma(asv_s_two, 1)`% when removing those ASVs that only appeared once and by between `r oxford_comma(asv_s_eleven, 1)`% when removing those that appeared ten or fewer times from each sample (Figure 2A). Similarly, the Shannon diversity decreased by between `r oxford_comma(asv_h_two, 1)`% when removing ASVs that only appeared once and by between `r oxford_comma(asv_s_eleven, 1)`% when removing ASVs that appeared ten or fewer times from each sample (Figure 2B). Next, I assigned the ASVs to OTUs to assess the impact of removing rare ASVs on higher level taxonomic groupings that are commonly used in microbial ecology studies. Although pooling similar ASVs into OTUs reduced the impact of removing the rare ASVs relative to the ASV-based analysis, the minimum abundance threshold still decreased the number of observed OTUs and the diversity decreased relative to the original community (**Figure S2AB**). In contrast to the number of ASVs or OTUs and their diversity, the Kullback–Leibler divergence compares the relative abundance of each ASV or OTU between representations of the community. I calculated the Kullback–Leibler divergence from the full to pruned communities when rare ASVs were removed. As the threshold for removing ASVs increased, the amount of information lost also increased for both ASVs and OTUs (Figure 2C and Figure S2C). The relative loss of information was generally lower for OTUs than than it was for ASVs. Removing rare ASVs, regardless of abundance threshold, had profound impacts on the representation of the communities.
